---
title: "Lab 2"
author: "Min Zhang, Hana Lee, Joshua Budi"
date: "2/23/2019"
output: html_document
---

Here is the link to our github [repo](https://github.com/MinZhang95/Lab-2)


```{r results='hide', message=FALSE, warning=FALSE} 
library(sf)
library(tidyverse)
library(purrr)
library(dplyr)
library(ggspatial)
```

#### Part 1: Todo for you: more map elements (slide 7)

- Plot of middle Earth: 

```{r}
p <- ggplot() +
  geom_sf(data = read_sf("data/ME-GIS/Coastline2.shp"), 
          colour="grey10", fill="grey90") +
  geom_sf(data = read_sf("data/ME-GIS/Rivers19.shp"), 
          colour="steelblue", size=0.3) +
  geom_sf(data = read_sf("data/ME-GIS/PrimaryRoads.shp"), 
          size = 0.7, colour="grey30") +
  geom_sf(data = read_sf("data/ME-GIS/Cities.shp")) +
  theme_bw()
p
```

- Add labels for the cities, a scale bar, arrow showing North.

```{r, message = FALSE, warning = FALSE}
p + annotation_scale(location="bl") +
  annotation_north_arrow(location="br")+ 
  geom_sf_text(data=read_sf("data/ME-GIS/Cities.shp"),
               mapping=aes(label=Name), size = 3)+
  theme_bw()
```

#### Part 2: Your Task (slide 16)

- Helper function to extract one matirix into a single data frame with variables `long`, `lat`, `group`, and `order`.

```{r, message=FALSE, warning=FALSE}
library("rgeos")
ozbig <- read_sf("data/gadm36_AUS_shp/gadm36_AUS_1.shp")
oz_st <- maptools::thinnedSpatialPoly(
  as(ozbig, "Spatial"), tolerance = 0.1, 
  minarea = 0.001, topologyPreserve = TRUE)
oz <- st_as_sf(oz_st)

# helper function turning one of these matrices into a single data frame
mat2df <- function(mat) {
  df <- data.frame(long = mat[, 1],
                   lat  = mat[, 2], 
                   temporary.group = sum(mat[,1]+mat[,2] *nrow(mat) + rnorm(1, 100, 10)), 
                   order= 1:nrow(mat))
  df
}
```

- Create a dataframe `ozplus` from the `geometry` variable using `purrr` functionality, and plot the result with the given code in the slide 16. (Map of Australia)

```{r}
# flatten oz$geometry twice to obtain a list of matrices
# this is because we have two layers of lists ahead of matrices
oz.geometry.flattened <- oz$geometry %>% flatten() %>% flatten()



# Create a dataframe ozplus from the geometry variable using purrr
# map_df applies a function to elements of a list and bind the dataframes together
# Instead of temporary.group variable by the function mat2df, 
# group variable consisting of the index corresponding each matrix will be used.
ozplus <- oz.geometry.flattened %>% purrr::map_df(.x = ., .id ="group", .f = mat2df)

# plot the result
ozplus %>% ggplot(aes(x = long, y = lat, group = group)) + geom_polygon()
```

- Test our code with another country: Map of China

```{r}
chnbig <- read_sf("data/gadm36_CHN_shp/gadm36_CHN_1.shp")
chn_st <- maptools::thinnedSpatialPoly(
  as(chnbig, "Spatial"), tolerance = 0.1, 
  minarea = 0.001, topologyPreserve = TRUE)
chn <- st_as_sf(chn_st)

chn.geometry.flattened <- chn$geometry %>% flatten() %>% flatten()
chnplus <- chn.geometry.flattened %>% purrr::map_df(.x = ., .id ="group", .f = mat2df)
chnplus %>% ggplot(aes(x = long, y = lat, group = group)) + geom_polygon()
```




